Title
========================================================

install.packages("knitr")

Load the data into R
```{r echo=TRUE}
actdata <- read.csv("C:/Users/Chris Curran.ThinkPadCC/Documents/GitHub/RepData_PeerAssessment1/activity.csv")
```

Clean data in preparation for graphing
```{r echo = TRUE}
install.packages("doBy")
library(doBy)
actdata_byday <- summaryBy(steps ~ date, FUN=c(mean, median), data=actdata)
```


Create a histogram of the total number of steps taken each day
```{r fig.width=7, fig.height=6}
hist(actdata_byday$steps.mean)
```

Output the mean and median number of steps taken per day
```{r}
actdata_byday
```

Create a dataset collapsed by the mean steps per time interval across days
```{r}
actdata_byinterval <- summaryBy(steps ~ interval, FUN=c(mean, median), data=actdata, na.rm = TRUE)
```

```{r}
plot(actdata_byinterval$interval, actdata_byinterval$steps.mean, type="l")
```
The 835 interval contains the most steps on average.

Counting the number of missing values.
```{r}
sum(is.na(actdata$steps))
```

Replace missing values with the overall mean
```{r}
actdata2<-actdata
actdata2$steps[is.na(actdata2$steps)] <- mean(actdata2$steps, na.rm=TRUE)

actdata2_byday <- summaryBy(steps ~ date, FUN=c(mean, median), data=actdata2)
```


Create a histogram of the total number of steps taken each day without missing values
```{r fig.width=7, fig.height=6}
hist(actdata2_byday$steps.mean)
```

The distribution looks roughly the same with and without the missing variables.

Since I used the overall average to impute, it pulled up the average for some days and pulled down the average for others.


Display the mean and median
```{r echo=TRUE}
actdata2_byday
```


Create a weekdays measure
```{r}

actdata2$day <- weekdays(as.Date(actdata2$date, "%Y-%m-%d"))
actdata2$weekday <- 1
actdata2$weekday[actdata2$day == "Sunday"] <- 0
actdata2$weekday[actdata2$day == "Saturday"] <- 0
actdata2weekday_byinterval <- summaryBy(steps ~ interval, FUN=c(mean, median), data=actdata2[actdata2$weekday ==1,])
actdata2weekend_byinterval <- summaryBy(steps ~ interval, FUN=c(mean, median), data=actdata2[actdata2$weekday ==0,])
```

Plot data by weekday status
```{r}
par(mfrow=c(2,1)) 
plot(actdata2weekday_byinterval$interval, actdata2weekday_byinterval$steps.mean, type="l")
plot(actdata2weekend_byinterval$interval, actdata2weekend_byinterval$steps.mean, type="l")
```


